---
title: "Session 4 Homework - PSYC6841 - Jaclyn Spangler"
output: html_notebook
---

# Objective
Using the Honeywell Glassdoor Comments from Class, create at least 20 comment categories. These can include subcategories (e.g. Benefits-Healthcare, Benefits-PTO, etc.). Run these over both the Pros and the Cons. You can create 2 different Excel sheets or 1 Excel sheet with one tab for Pros and one tab for Cons.

## Resources

* [link1](https://stackoverflow.com/questions/26319567/use-grepl-to-search-either-of-multiple-substrings-in-a-text)
* [lnk2](https://stackoverflow.com/questions/5823503/pattern-matching-using-a-wildcard)
* [link3](https://stackoverflow.com/questions/31421077/r-wildcard-matching-for-certain-number-of-terms)
* [link4](https://www.regular-expressions.info/rlanguage.html)

# Notebook Setup

```{r Libraries}
tryCatch(require(pacman),finally=utils:::install.packages(pkgs='pacman',repos='http://cran.r-project.org'));
require(pacman)

pacman::p_load(openxlsx, 
               tidyverse, 
               devtools,
               conflicted,
               lubridate,
               sentimentr)

#Loading libraries
library(openxlsx)
library(tidyverse)
library(devtools)
library(conflicted)
library(lubridate)
library(sentimentr)
# devtools::install_github("mguideng/gdscrapeR")
# library(gdscrapeR)

conflict_prefer("filter", "dplyr")
```


# Loading & Configuring Data 

```{r Honeywell Glassdoor Data}
library(readr)
Data <- read_csv("C:/Users/Jaclyn/Desktop/LearningR/AdvAnalytics/00_data/glassdoortest1.csv")
```


```{r Col Names}
colnames(Data)
```


```{r Name ID variable}
#Change X1 to ID

Data <- Data %>%
    rename(ID = X1)
```

## Check for Duplicates

I noticed there were a lot of duplicates while working with this data. Removing the duplicate entries. 

```{r}
#Checking for duplicates on multiple columns
#Specifically on multiple entries per agent per month
which(duplicated(Data[c("pros", "cons")]))

index <- which(duplicated(Data[c("pros", "cons")]))

Data <- Data[-index, ]

```


```{r Dataframes}
# Creating new dataframes for Pros & Cons

df_pro_comments <- Data %>%
    select(c(ID, pros)) %>%
    filter(!is.na(pros)) %>%
    rename('comments' = 'pros')

###
df_con_comments <- Data %>%
    select(c(ID, cons)) %>%
    filter(!is.na(cons)) %>%
    rename('comments' = 'cons')

```


```{r Lowercase}
#Converting to lower case

df_pro_comments <- df_pro_comments %>%
    mutate(comments = tolower(comments))

df_con_comments <- df_con_comments %>%
    mutate(comments = tolower(comments))

```


```{r Line breaks}
#Remove all line breaks

#From: https://stackoverflow.com/questions/21781014/remove-all-line-breaks-enter-symbols-from-the-string-using-r

df_pro_comments$comments <- gsub("[\r\n]", "", df_pro_comments$comments)

df_pro_comments <- df_pro_comments %>%
    select(ID, comments) %>%
    na.omit()

###
df_con_comments$comments <- gsub("[\r\n]", "", df_con_comments$comments)

df_con_comments <- df_con_comments %>%
    select(ID, comments) %>%
    na.omit()

```


# Code Optimization - Start Time

```{r Start Time}
#Creating a beginning using `now` from lubridate.
#This is helpful when you get to several categories using a brute force search so that you (and others if they run you script) know about how long it will take to run.

#After we run everything, we will create `end_time <- now()` along with `print(difftime(end_time, start_time))` as the last line of code after everything we are concerned about has run.

start_time <- now()
```



# Creating Categories

## Category 1: Healthcare

```{r Health Benefits}
## IDENTIFY SEARCH PARAMETERS ##
health <- c('\\brx\\b', #this will only get the word "rx" and nothing else
              '^.*medic.*$', #this will get medic, medicine, medical, etc.
              '(?=.*bene)(?=.*(?:health))', #This will get benefits, beneficial, benefit, etc. but only if it occurs with health, healthy, healthcare, in the same comment
              '(?=.*coverage)(?=.*(?:medic|deduct|prescrip|insur|drug|health|dependent))', #This will get coverage, overages, etc. as long as some form of medic, deduct, prescription, etc. occur in the same comment
                    '\\b(?:health\\W+(?:\\w+\\W+){0,1}?care)\\b', #this will only get health care or healthcare (e.g. health and care must occur within one word)
                    '\\bhealthcare\\b', #this will only get the word "healthcare". If there is a space between them, it won't pick it up.
              '\\bhealth\\s?care\\b', #this will get the word "healthcare" or "health care" as the \\s? indicates zero or one whitespace character.
              '\\b(?:medical\\W+(?:\\w+\\W+){0,3}?benefits|benefits\\W+(?:\\w+\\W+){0,3}?medical)\\b', #This will get medical benefits or benefits medical as long as they occur within 3 word of each other.
              '^.*vacation.*$',
              '\\bpto\\b',  #just the word pto
              '\\bbenefits\\b' #just the word benefits
              )

## CREATE PATTERN ##
health_pattern <- paste(health, collapse = "|") #Benefits pattern for searching

## PRO- SEARCH & CREATE ##
health_comments_pro <- as.data.frame(df_pro_comments[grep(health_pattern, df_pro_comments$comments, value = FALSE, perl = TRUE),]) #Search Pro Comments

TEST_pro <- df_pro_comments %>%
    mutate(health = ifelse(comments %in% health_comments_pro$comments, "Y",
                             "N")) 
## CON- SEARCH & CREATE ##
health_comments_con <- as.data.frame(df_con_comments[grep(health_pattern, df_con_comments$comments, value = FALSE, perl = TRUE),]) #Search Con Comments

TEST_con <- df_con_comments %>%
    mutate(health = ifelse(comments %in% health_comments_con$comments, "Y",
                             "N"))
```

## Category 2: Insurance

```{r Insurance}
## IDENTIFY SEARCH PARAMETERS ##
insurance <- c('(?=.*insur)(?=.*(?:medic|dental|life|vision|supplement|disabl))',
                        '\\b(?:insurance\\W+(?:\\w+\\W+){0,1}?premium)\\b',
                        '\\binsurance\\b'
                        )

## CREATE PATTERN ##
insurance_pattern <- paste(insurance, collapse = "|") 

## PRO- SEARCH & CREATE ##
insurance_comments_pro <- as.data.frame(df_pro_comments[grep(insurance_pattern, df_pro_comments$comments, value = FALSE, perl = TRUE),]) #Search Pro Comments


TEST_pro <- TEST_pro %>%
    mutate(insurance = ifelse(comments %in%
                                         insurance_comments_pro$comments,
                                       "Y",
                                       "N"))
## CON- SEARCH & CREATE ##
insurance_comments_con <- as.data.frame(df_con_comments[grep(insurance_pattern, df_con_comments$comments, value = FALSE, perl = TRUE),]) #Search Con Comments

TEST_con <- TEST_con %>%
    mutate(insurance = ifelse(comments %in%
                                         insurance_comments_con$comments,
                                       "Y",
                                       "N"))
```

## Category 3: Compensation

```{r Compensation}
## IDENTIFY SEARCH PARAMETERS ##
compensation <- c('\\bsalary\\b', 
              '^.*compen.*$',
              '\\bpay\\b',
              '\\bwage\\b' 
                     )

## CREATE PATTERN ##
compensation_pattern <- paste(compensation, collapse = "|") #Create category pattern

## PRO- SEARCH & CREATE ##
compensation_comments_pro <- as.data.frame(df_pro_comments[grep(compensation_pattern, df_pro_comments$comments, value = FALSE, perl = TRUE),]) #Search Pro Comments


TEST_pro <- TEST_pro %>%
    mutate(compensation = ifelse(comments %in%
                                         compensation_comments_pro$comments,
                                       "Y",
                                       "N"))
## CON- SEARCH & CREATE ##
compensation_comments_con <- as.data.frame(df_con_comments[grep(compensation_pattern, df_con_comments$comments, value = FALSE, perl = TRUE),]) #Search Con Comments

TEST_con <- TEST_con %>%
    mutate(compensation = ifelse(comments %in%
                                         compensation_comments_con$comments,
                                       "Y",
                                       "N"))
```

## Category 4: Culture

```{r Culture}
## IDENTIFY SEARCH PARAMETERS ##
culture <- c('\\bculture\\b',
             '^.*culture.*$',
             '\\bwork\\s?environment\\b',
             '\\bworking\\s?environment\\b',
             '\\*?workplace?'
                     )

## CREATE PATTERN ##
culture_pattern <- paste(culture, collapse = "|") #Create category pattern

## PRO- SEARCH & CREATE ##
culture_comments_pro <- as.data.frame(df_pro_comments[grep(culture_pattern, df_pro_comments$comments, value = FALSE, perl = TRUE),]) #Search Pro Comments


TEST_pro <- TEST_pro %>%
    mutate(culture = ifelse(comments %in% culture_comments_pro$comments,
                                       "Y",
                                       "N"))
## CON- SEARCH & CREATE ##
culture_comments_con <- as.data.frame(df_con_comments[grep(culture_pattern, df_con_comments$comments, value = FALSE, perl = TRUE),]) #Search Con Comments

TEST_con <- TEST_con %>%
    mutate(culture = ifelse(comments %in% culture_comments_con$comments,
                                       "Y",
                                       "N"))
```

## Category 5: Leadership

```{r Leadership}
## IDENTIFY SEARCH PARAMETERS ##
leadership <- c('\\bceo\\b',
                '\\*?leadership?',
                '\\*?leader?',
                '\\*?executive*\\b'
                     )

## CREATE PATTERN ##
leadership_pattern <- paste(leadership, collapse = "|") #Create category pattern

## PRO- SEARCH & CREATE ##
leadership_comments_pro <- as.data.frame(df_pro_comments[grep(leadership_pattern, df_pro_comments$comments, value = FALSE, perl = TRUE),]) #Search Pro Comments


TEST_pro <- TEST_pro %>%
    mutate(leadership = ifelse(comments %in% leadership_comments_pro$comments,
                                       "Y",
                                       "N"))
## CON- SEARCH & CREATE ##
leadership_comments_con <- as.data.frame(df_con_comments[grep(leadership_pattern, df_con_comments$comments, value = FALSE, perl = TRUE),]) #Search Con Comments

TEST_con <- TEST_con %>%
    mutate(leadership = ifelse(comments %in% leadership_comments_con$comments,
                                       "Y",
                                       "N"))
```

## Category 6: Management
Manager, Boss, direct manager, upper management

```{r Management}
## IDENTIFY SEARCH PARAMETERS ##
management <- c('\\bmanagement\\b',
                '\\*?management?',
                '\\bmanager*\\b',
                '\\bboss\\b'
                )

## CREATE PATTERN ##
management_pattern <- paste(management, collapse = "|") #Create category pattern

## PRO- SEARCH & CREATE ##
management_comments_pro <- as.data.frame(df_pro_comments[grep(management_pattern, df_pro_comments$comments, value = FALSE, perl = TRUE),]) #Search Pro Comments


TEST_pro <- TEST_pro %>%
    mutate(management = ifelse(comments %in% management_comments_pro$comments,
                                       "Y",
                                       "N"))
## CON- SEARCH & CREATE ##
management_comments_con <- as.data.frame(df_con_comments[grep(management_pattern, df_con_comments$comments, value = FALSE, perl = TRUE),]) #Search Con Comments

TEST_con <- TEST_con %>%
    mutate(management = ifelse(comments %in% management_comments_con$comments,
                                       "Y",
                                       "N"))
```

## Category 7: Career Advancement
Move around, career, mobility, promotion, promoted, Room to grow

```{r Career}
## IDENTIFY SEARCH PARAMETERS ##
career <- c('\\bcareer\\b',
            '\\bmobility\\b',
            '\\bpromotion\\b',
            '^.*promot.*$',
            'room to grow'
                     )

## CREATE PATTERN ##
career_pattern <- paste(career, collapse = "|") #Create category pattern

## PRO- SEARCH & CREATE ##
career_comments_pro <- as.data.frame(df_pro_comments[grep(career_pattern, df_pro_comments$comments, value = FALSE, perl = TRUE),]) #Search Pro Comments


TEST_pro <- TEST_pro %>%
    mutate(career = ifelse(comments %in% career_comments_pro$comments,
                                       "Y",
                                       "N"))
## CON- SEARCH & CREATE ##
career_comments_con <- as.data.frame(df_con_comments[grep(career_pattern, df_con_comments$comments, value = FALSE, perl = TRUE),]) #Search Con Comments

TEST_con <- TEST_con %>%
    mutate(career = ifelse(comments %in% career_comments_con$comments,
                                       "Y",
                                       "N"))
```

## Category 8: Work Life Balance
Work life, , Burnout, Work balance, Flexibility, Freedom

```{r Work Life Balance}
## IDENTIFY SEARCH PARAMETERS ##
wlb <- c('\\bhours\\b',
         '\\bburnout\\b',
         '\\bflexibility\\b',
         '\\bfreedom\\b',
         'work balance',
         'work life',
         '^.*flex.*$'
                     )

## CREATE PATTERN ##
wlb_pattern <- paste(wlb, collapse = "|") #Create category pattern

## PRO- SEARCH & CREATE ##
wlb_comments_pro <- as.data.frame(df_pro_comments[grep(wlb_pattern, df_pro_comments$comments, value = FALSE, perl = TRUE),]) #Search Pro Comments


TEST_pro <- TEST_pro %>%
    mutate(wlb = ifelse(comments %in% wlb_comments_pro$comments,
                                       "Y",
                                       "N"))
## CON- SEARCH & CREATE ##
wlb_comments_con <- as.data.frame(df_con_comments[grep(wlb_pattern, df_con_comments$comments, value = FALSE, perl = TRUE),]) #Search Con Comments

TEST_con <- TEST_con %>%
    mutate(wlb = ifelse(comments %in% wlb_comments_con$comments,
                                       "Y",
                                       "N"))
```

## Category 9: Morale

```{r Morale}
## IDENTIFY SEARCH PARAMETERS ##
morale <- c('\\bmorale\\b'
                     )

## CREATE PATTERN ##
morale_pattern <- paste(morale, collapse = "|") #Create category pattern

## PRO- SEARCH & CREATE ##
morale_comments_pro <- as.data.frame(df_pro_comments[grep(morale_pattern, df_pro_comments$comments, value = FALSE, perl = TRUE),]) #Search Pro Comments


TEST_pro <- TEST_pro %>%
    mutate(morale = ifelse(comments %in% morale_comments_pro$comments,
                                       "Y",
                                       "N"))
## CON- SEARCH & CREATE ##
morale_comments_con <- as.data.frame(df_con_comments[grep(morale_pattern, df_con_comments$comments, value = FALSE, perl = TRUE),]) #Search Con Comments

TEST_con <- TEST_con %>%
    mutate(morale = ifelse(comments %in% morale_comments_con$comments,
                                       "Y",
                                       "N"))
```

## Category 10: Product & Innovation
Product, Technology, Systems, Innovation / Innovative

```{r Product}
## IDENTIFY SEARCH PARAMETERS ##
product <- c('\\bproduct\\b',
             '\\btechnology\\b',
             '\\bsystems\\b',
             '\\binnovat.*$'
                     )

## CREATE PATTERN ##
product_pattern <- paste(product, collapse = "|") #Create category pattern

## PRO- SEARCH & CREATE ##
product_comments_pro <- as.data.frame(df_pro_comments[grep(product_pattern, df_pro_comments$comments, value = FALSE, perl = TRUE),]) #Search Pro Comments


TEST_pro <- TEST_pro %>%
    mutate(product = ifelse(comments %in% product_comments_pro$comments,
                                       "Y",
                                       "N"))
## CON- SEARCH & CREATE ##
product_comments_con <- as.data.frame(df_con_comments[grep(product_pattern, df_con_comments$comments, value = FALSE, perl = TRUE),]) #Search Con Comments

TEST_con <- TEST_con %>%
    mutate(product = ifelse(comments %in% product_comments_con$comments,
                                       "Y",
                                       "N"))
```


## Category 11: Work from Home
Work from home, Remote, Telecommute

```{r WFH}
## IDENTIFY SEARCH PARAMETERS ##
wfh <- c('work from home',
         '\\bremote\\b',
         '\\btelecommut.*$'
                     )

## CREATE PATTERN ##
wfh_pattern <- paste(wfh, collapse = "|") #Create category pattern

## PRO- SEARCH & CREATE ##
wfh_comments_pro <- as.data.frame(df_pro_comments[grep(wfh_pattern, df_pro_comments$comments, value = FALSE, perl = TRUE),]) #Search Pro Comments


TEST_pro <- TEST_pro %>%
    mutate(wfh = ifelse(comments %in% wfh_comments_pro$comments,
                                       "Y",
                                       "N"))
## CON- SEARCH & CREATE ##
wfh_comments_con <- as.data.frame(df_con_comments[grep(wfh_pattern, df_con_comments$comments, value = FALSE, perl = TRUE),]) #Search Con Comments

TEST_con <- TEST_con %>%
    mutate(wfh = ifelse(comments %in% wfh_comments_con$comments,
                                       "Y",
                                       "N"))
```

## Category 12: Co-Workers
People, Colleagues, co-workers

```{r Colleagues }
## IDENTIFY SEARCH PARAMETERS ##
colleagues <- c('\\bcolleague.*$',
                '\\bco\\D?work.*$',
                '\\bpeople\\b'
                     )

## CREATE PATTERN ##
colleagues_pattern <- paste(colleagues, collapse = "|") #Create category pattern

## PRO- SEARCH & CREATE ##
colleagues_comments_pro <- as.data.frame(df_pro_comments[grep(colleagues_pattern, df_pro_comments$comments, value = FALSE, perl = TRUE),]) #Search Pro Comments


TEST_pro <- TEST_pro %>%
    mutate(colleagues = ifelse(comments %in% colleagues_comments_pro$comments,
                                       "Y",
                                       "N"))
## CON- SEARCH & CREATE ##
colleagues_comments_con <- as.data.frame(df_con_comments[grep(colleagues_pattern, df_con_comments$comments, value = FALSE, perl = TRUE),]) #Search Con Comments

TEST_con <- TEST_con %>%
    mutate(colleagues = ifelse(comments %in% colleagues_comments_con$comments,
                                       "Y",
                                       "N"))
```

## Category 13: Mission & Goals
Mission, Goals, Strategy

```{r Mission}
## IDENTIFY SEARCH PARAMETERS ##
mission <- c('\\bmission\\b',
             '\\bgoals\\b',
             '\\bstrateg.*$'
                     )

## CREATE PATTERN ##
mission_pattern <- paste(mission, collapse = "|") #Create category pattern

## PRO- SEARCH & CREATE ##
mission_comments_pro <- as.data.frame(df_pro_comments[grep(mission_pattern, df_pro_comments$comments, value = FALSE, perl = TRUE),]) #Search Pro Comments


TEST_pro <- TEST_pro %>%
    mutate(mission = ifelse(comments %in% mission_comments_pro$comments,
                                       "Y",
                                       "N"))
## CON- SEARCH & CREATE ##
mission_comments_con <- as.data.frame(df_con_comments[grep(mission_pattern, df_con_comments$comments, value = FALSE, perl = TRUE),]) #Search Con Comments

TEST_con <- TEST_con %>%
    mutate(mission = ifelse(comments %in% mission_comments_con$comments,
                                       "Y",
                                       "N"))
```

## Category 14: Overtime

```{r Overtime}
## IDENTIFY SEARCH PARAMETERS ##
overtime <- c('\\bovertime\\b'
                     )

## CREATE PATTERN ##
overtime_pattern <- paste(overtime, collapse = "|") #Create category pattern

## PRO- SEARCH & CREATE ##
overtime_comments_pro <- as.data.frame(df_pro_comments[grep(overtime_pattern, df_pro_comments$comments, value = FALSE, perl = TRUE),]) #Search Pro Comments


TEST_pro <- TEST_pro %>%
    mutate(overtime = ifelse(comments %in% overtime_comments_pro$comments,
                                       "Y",
                                       "N"))
## CON- SEARCH & CREATE ##
overtime_comments_con <- as.data.frame(df_con_comments[grep(overtime_pattern, df_con_comments$comments, value = FALSE, perl = TRUE),]) #Search Con Comments

TEST_con <- TEST_con %>%
    mutate(overtime = ifelse(comments %in% overtime_comments_con$comments,
                                       "Y",
                                       "N"))
```

## Category 15: Interesting Work

```{r }
## IDENTIFY SEARCH PARAMETERS ##
interesting <- c('\\b(?:interesting|meaningful|challenging\\W+(?:\\w+\\W+){0,3}?work\\D?|projects\\W+(?:\\w+\\W+){0,3}?medical)\\b'
                     )

## CREATE PATTERN ##
interesting_pattern <- paste(interesting, collapse = "|") #Create category pattern

## PRO- SEARCH & CREATE ##
interesting_comments_pro <- as.data.frame(df_pro_comments[grep(interesting_pattern, df_pro_comments$comments, value = FALSE, perl = TRUE),]) #Search Pro Comments


TEST_pro <- TEST_pro %>%
    mutate(interesting = ifelse(comments %in% interesting_comments_pro$comments,
                                       "Y",
                                       "N"))
## CON- SEARCH & CREATE ##
interesting_comments_con <- as.data.frame(df_con_comments[grep(interesting_pattern, df_con_comments$comments, value = FALSE, perl = TRUE),]) #Search Con Comments

TEST_con <- TEST_con %>%
    mutate(interesting = ifelse(comments %in% interesting_comments_con$comments,
                                       "Y",
                                       "N"))
```

## Category 16: Team Dynamics
team, teamwork

```{r }
## IDENTIFY SEARCH PARAMETERS ##
team <- c('\\bteamwork\\b',
          '\\bteam\\D?work.*$',
          '\\bteams?'
                     )

## CREATE PATTERN ##
team_pattern <- paste(team, collapse = "|") #Create category pattern

## PRO- SEARCH & CREATE ##
team_comments_pro <- as.data.frame(df_pro_comments[grep(team_pattern, df_pro_comments$comments, value = FALSE, perl = TRUE),]) #Search Pro Comments


TEST_pro <- TEST_pro %>%
    mutate(team = ifelse(comments %in% team_comments_pro$comments,
                                       "Y",
                                       "N"))
## CON- SEARCH & CREATE ##
team_comments_con <- as.data.frame(df_con_comments[grep(team_pattern, df_con_comments$comments, value = FALSE, perl = TRUE),]) #Search Con Comments

TEST_con <- TEST_con %>%
    mutate(team = ifelse(comments %in% team_comments_con$comments,
                                       "Y",
                                       "N"))
```

## Category 17: Resources
Resources, Funding

```{r Resources}
## IDENTIFY SEARCH PARAMETERS ##
resources <- c('\\bresources?',
                '\\bfunding\\b'
                     )

## CREATE PATTERN ##
resources_pattern <- paste(resources, collapse = "|") #Create category pattern

## PRO- SEARCH & CREATE ##
resources_comments_pro <- as.data.frame(df_pro_comments[grep(resources_pattern, df_pro_comments$comments, value = FALSE, perl = TRUE),]) #Search Pro Comments


TEST_pro <- TEST_pro %>%
    mutate(resources = ifelse(comments %in% resources_comments_pro$comments,
                                       "Y",
                                       "N"))
## CON- SEARCH & CREATE ##
resources_comments_con <- as.data.frame(df_con_comments[grep(resources_pattern, df_con_comments$comments, value = FALSE, perl = TRUE),]) #Search Con Comments

TEST_con <- TEST_con %>%
    mutate(resources = ifelse(comments %in% resources_comments_con$comments,
                                       "Y",
                                       "N"))
```

## Category 18: Process
Efficiency, Inefficiencies, Red tape, Beauracracy, Efficient

```{r Process}
## IDENTIFY SEARCH PARAMETERS ##
process <- c('\\befficien.*$',
             '\\bineffecien.*$',
             '\\bred.tape\\b',
             '\\bbeauracra\\*?',
             '\\bprocesse?s?',
             '\\bdecision.making\\b'
                     )

## CREATE PATTERN ##
process_pattern <- paste(process, collapse = "|") #Create category pattern

## PRO- SEARCH & CREATE ##
process_comments_pro <- as.data.frame(df_pro_comments[grep(process_pattern, df_pro_comments$comments, value = FALSE, perl = TRUE),]) #Search Pro Comments


TEST_pro <- TEST_pro %>%
    mutate(process = ifelse(comments %in% process_comments_pro$comments,
                                       "Y",
                                       "N"))
## CON- SEARCH & CREATE ##
process_comments_con <- as.data.frame(df_con_comments[grep(process_pattern, df_con_comments$comments, value = FALSE, perl = TRUE),]) #Search Con Comments

TEST_con <- TEST_con %>%
    mutate(process = ifelse(comments %in% process_comments_con$comments,
                                       "Y",
                                       "N"))
```

## Category 19: RIFs & Furloughs
RIF, furlough

```{r RIF}
## IDENTIFY SEARCH PARAMETERS ##
rif <- c('\\brif*?',
         '\\bfurlough*?'
                     )

## CREATE PATTERN ##
rif_pattern <- paste(rif, collapse = "|") #Create category pattern

## PRO- SEARCH & CREATE ##
rif_comments_pro <- as.data.frame(df_pro_comments[grep(rif_pattern, df_pro_comments$comments, value = FALSE, perl = TRUE),]) #Search Pro Comments


TEST_pro <- TEST_pro %>%
    mutate(rif = ifelse(comments %in% rif_comments_pro$comments,
                                       "Y",
                                       "N"))
## CON- SEARCH & CREATE ##
rif_comments_con <- as.data.frame(df_con_comments[grep(rif_pattern, df_con_comments$comments, value = FALSE, perl = TRUE),]) #Search Con Comments

TEST_con <- TEST_con %>%
    mutate(rif = ifelse(comments %in% rif_comments_con$comments,
                                       "Y",
                                       "N"))

```

## Category 20: Other 

```{r Other}
TEST_pro <- TEST_pro %>%
    mutate(Other = apply(TEST_pro, 1, function(y){ ifelse("Y" %in% y, "N", "Y")}))

TEST_con <- TEST_con %>%
    mutate(Other = apply(TEST_con, 1, function(y){ ifelse("Y" %in% y, "N", "Y")}))
```


``` {r Measure Time}
#CLOSE OUT
end_time <- now()

print(difftime(end_time, start_time))
```


# Combining Subcategories into Meta Categories

```{r}
#Export for categorization
# write.xlsx(TEST_con, "C:/Users/Jaclyn/Desktop/test_con.xlsx", sheetName = "Sheet1", 
#   col.names = TRUE, row.names = TRUE, append = FALSE)
```

```{r Categorization}
#NESTED IF/ELSE TO TURN INTO CATEGORIES

#PRO
TEST_pro <- TEST_pro %>%
    mutate(Benefits = ifelse(health == "Y", "Y",
                             ifelse(insurance == "Y", "Y",
                                    ifelse(compensation == "Y", "Y",
                                           ifelse(wfh == "Y", "Y",
                                     "N"))))) 
TEST_pro <- TEST_pro %>%
    mutate(Climate = ifelse(culture == "Y", "Y",
                             ifelse(career == "Y", "Y",
                                    ifelse(wlb == "Y", "Y",
                                           ifelse(morale == "Y", "Y",
                                                  ifelse(rif == "Y", "Y",
                                     "N")))))) 
TEST_pro <- TEST_pro %>%
    mutate(DailyWork = ifelse(colleagues == "Y", "Y",
                             ifelse(overtime == "Y", "Y",
                                    ifelse(interesting == "Y", "Y",
                                           ifelse(resources == "Y", "Y",
                                                  ifelse(team == "Y", "Y",
                                                         ifelse(process == "Y", "Y",
                                     "N"))))))) 
TEST_pro <- TEST_pro %>%
    mutate(Company = ifelse(leadership == "Y", "Y",
                             ifelse(management == "Y", "Y",
                                    ifelse(product == "Y", "Y",
                                           ifelse(mission == "Y", "Y",
                                     "N"))))) 

#CON
TEST_con <- TEST_con %>%
    mutate(Benefits = ifelse(health == "Y", "Y",
                             ifelse(insurance == "Y", "Y",
                                    ifelse(compensation == "Y", "Y",
                                           ifelse(wfh == "Y", "Y",
                                     "N"))))) 
TEST_con <- TEST_con %>%
    mutate(Climate = ifelse(culture == "Y", "Y",
                             ifelse(career == "Y", "Y",
                                    ifelse(wlb == "Y", "Y",
                                           ifelse(morale == "Y", "Y",
                                                  ifelse(rif == "Y", "Y",
                                     "N")))))) 
TEST_con <- TEST_con %>%
    mutate(DailyWork = ifelse(colleagues == "Y", "Y",
                             ifelse(overtime == "Y", "Y",
                                    ifelse(interesting == "Y", "Y",
                                           ifelse(resources == "Y", "Y",
                                                  ifelse(team == "Y", "Y",
                                                         ifelse(process == "Y", "Y",
                                     "N"))))))) 
TEST_con <- TEST_con %>%
    mutate(Company = ifelse(leadership == "Y", "Y",
                             ifelse(management == "Y", "Y",
                                    ifelse(product == "Y", "Y",
                                           ifelse(mission == "Y", "Y",
                                     "N"))))) 

```

```{r}
#REORDER COLUMNS BY CATEGORY
colnames(TEST_con)
```

```{r}

col_order<- c("ID", "comments", "Benefits", "health", "insurance", "compensation", "wfh", "Climate","career", "culture", "wlb", "morale", "rif", "Company", "leadership", "management", "mission", "product", "DailyWork", "overtime", "resources", "process", "team", "colleagues", "interesting", "Other")

FINAL_pro <- TEST_pro[, col_order]

FINAL_con <- TEST_pro[, col_order]
```


<!-- # Category Summary -->

```{r Category Table}
#TAKE A LOOK AT THE DATA YOU'VE GATHERED
#Start answering questions like, "Of the total comments, XX% mentioned benefits. Of those, XX% were about compensation, which seems to be a key blah blah blah. Out of all of the 2000 comments, XX% are about compensation."

# TEST %>% tabyl(Benefits_Overall)
```



# Finalize Report in Excel

```{r Write to Excel}

#Also check here: https://stackoverflow.com/questions/37677326/applying-style-to-all-sheets-of-a-workbook-using-openxlsx-package-in-r


##################################
# Glassdoor Reviews Categorized Report
##################################

#Creating df for header

INTRO <- c("Honeywell",

         "Data Source: Glassdoor",

         "Data As Of: June 2021",

         "Prepared on: 7/23/2021",

         "Prepared by: Jaclyn Spangler")

wb <- openxlsx::createWorkbook() #Create a work book

#CREATE WB & COMMENTS TABS

addWorksheet(wb, "PRO Comments") #name the worksheet in Excel
writeData(wb, "PRO Comments", INTRO) #Write your INTRO

addWorksheet(wb, "CON Comments") #name the worksheet in Excel
writeData(wb, "CON Comments", INTRO) #Write your INTRO


#STYLE

style1 <- createStyle(fontColour = "#349891", textDecoration = "Bold") #Fnt Colors (https://www.rgbtohex.net/) and make it bold. Call it style1

addStyle(wb, style = style1, rows= 1:5, cols = 1, sheet = "PRO Comments") 
addStyle(wb, style = style1, rows= 1:5, cols = 1, sheet = "CON Comments") #add this style to your worksheet. Tell it which rows and columns

hs1 <- createStyle(textDecoration = "Bold") #create a new style for heading

addStyle(wb, style = hs1, rows = 8, cols = 1:50, sheet = "PRO Comments") 
addStyle(wb, style = hs1, rows = 8, cols = 1:50, sheet = "CON Comments") 

style2 <- createStyle(fgFill = "#8CD8D3") #Fill Color for category columns

# Couldn't get a list of columns to work, so doing it the hard way...
addStyle(wb, style = style2, rows= 8:2008, cols = 3, sheet = "PRO Comments") 
addStyle(wb, style = style2, rows= 8:2008, cols = 8, sheet = "PRO Comments") 
addStyle(wb, style = style2, rows= 8:2008, cols = 14, sheet = "PRO Comments") 
addStyle(wb, style = style2, rows= 8:2008, cols = 19, sheet = "PRO Comments") 
addStyle(wb, style = style2, rows= 8:2008, cols = 26, sheet = "PRO Comments") 

addStyle(wb, style = style2, rows= 8:2008, cols = 3, sheet = "CON Comments") 
addStyle(wb, style = style2, rows= 8:2008, cols = 8, sheet = "CON Comments") 
addStyle(wb, style = style2, rows= 8:2008, cols = 14, sheet = "CON Comments") 
addStyle(wb, style = style2, rows= 8:2008, cols = 19, sheet = "CON Comments") 
addStyle(wb, style = style2, rows= 8:2008, cols = 26, sheet = "CON Comments") 

#WRITE DATE TO SHEETS

writeData(wb, "PRO Comments", FINAL_pro, startRow = 8)
writeData(wb, "CON Comments", FINAL_con, startRow = 8) 

#FREEZE PANES IN SHEETS

freezePane(wb, "PRO Comments", firstActiveRow = 9)
freezePane(wb, "CON Comments", firstActiveRow = 9)

#ADD FILTER TO SHEETS

addFilter(wb, "PRO Comments", row = 8, cols = 1:50) 
addFilter(wb, "CON Comments", row = 8, cols = 1:50) 

#SET COLUMN WIDTH FOR COMMENTS & WRAP
setColWidths(wb, "PRO Comments", cols = 2, widths = 75) 
setColWidths(wb, "CON Comments", cols = 2, widths = 75) 

style3 <- createStyle(wrapText = TRUE)

addStyle(wb, "PRO Comments", style3, rows = 8:2008, cols = 2, gridExpand = TRUE)
addStyle(wb, "CON Comments", style3, rows = 8:2008, cols = 2, gridExpand = TRUE)


#SAVE FILE AND ADD DATE TO TITLE

saveWorkbook(wb, paste0("C:/Users/Jaclyn/Desktop/GithubClone/psyc6841_hw4/Glassdoor Categorized Comments_", format(floor_date(Sys.Date()-months(1), "month"), "%B_%Y") , ".xlsx"), overwrite = TRUE)
```
